Response to Reviewers and Associate Editor

### 2021-10-07 paper/changes.tex
minor change in the language regarding SSIM.

 \begin{itemize}
 \item    \textcolor{blue}{...the paper should at least include a (short) discussion about the
     possibility of using deep learning for this, and its disadvantages.}

@@

  We have now presented RMSE values for all reconstructions in Tables 1-5 of the main paper. Since RMSE corresponds to error in intensity values, we have used SSIM with a higher weightage to structure for the purpose of measuring error in preservation of structures in our reconstructions.
  \begin{comment}
  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{Eq:simple_TV}.

@@

  \end{itemize}

>>>>

 \begin{enumerate}
 \item    \textcolor{blue}{...the paper should at least include a (short) discussion about the
     possibility of using deep learning for this, and its disadvantages.}

@@

We accept the criticism, and have now presented both RMSE and SSIM
values for all reconstructions in Tables 1-5 of the main paper. 
  \begin{comment}
Since
RMSE corresponds to error in intensity values, we have used SSIM with
a higher weightage to structure for the purpose of measuring error in
preservation of structures in our reconstructions.

  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{Eq:simple_TV}.

@@

\end{enumerate}
